Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-04-10 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
update for Tropical Andes and species list

# Create species list from IUCN data
```{r}
frugivore_species <- unique(frugivore_habitats$scientificName)
```

@@

# Download data
```{r}
occ_download(
pred_in("taxonKey", gbif_taxon_keys), # important to use pred_in
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE")), 
format = "SIMPLE_CSV"
)
```

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0149390-230224095556074", path = output_path) %>%
  occ_download_import()
```

>>>>

# Create species list from IUCN data
```{r}
frugivore_species <- unique(frugivore_habitats$scientificName)
write.csv2(frugivore_species, file = file.path(output_path, "TropicalFrugivoreSpecies.csv"))
```

@@

# Download data
```{r}
occ_download(
pred_in("taxonKey", gbif_taxon_keys),
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")), 
format = "SIMPLE_CSV"
)
```

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0154158-230224095556074", path = output_path) %>%
  occ_download_import()
```
